### 2020-12-04 05_Thesis/THESIS_LaTeX/main.tex
paper work

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Search for high-molecular weight linear polymers for the formulation of novel solutions for the fabrication of micro fibers by electromechanical spinning}
% Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon

>>>>

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Search for High-Molecular Weight Linear Polymers for the Formulation of Novel Solutions for the Fabrication of Micro-Fibers by Electromechanical Spinning}
% Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon
